---
author: "Florian Fox"
date: "`r Sys.Date()`"
title: 'Master Thesis: A Causal Test of the Law of 1/n and its Mechanisms -- Analysis: RDD, Normalized Cutoff, Investigating the Heterogeneity'
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---



# Load data and packages

```{r Packages}
time <- Sys.time()
library(tidyverse)
library(fixest)
library(rdrobust)
#library(rdmulti)
library(rddensity)
#library(rdd) # For the McCrary (2008) test
#library(xtable)
#library(scales)
#library(janitor)
library(ggpubr)
library(stringr)
source("functions/functions.R")
```

```{r Data}
data <-
  readRDS("data/gemeinderatswahlen_alldata.rds") %>%
  filter(year <= 2014) %>%
  mutate(
    year = as.factor(year),
    ags = as.factor(ags)
  ) %>%
  # Repeat (bandwidth) window calculation for data subsets
  mutate(
    closest = base::rank(abs(inhabs_rel_to_cutoff), ties.method = "last"),
    closest = closest/max(closest),
  )
```

Additional functions:

```{r}
rdrobust_wrapper <- function(ccluster = NULL, ccovs = NULL) {
  rdrobust::rdrobust(
      y = df$ln_gross_expenditure_pc,
      x = df$inhabs_rel_to_cutoff,
      fuzzy = df$total_seats,
      cluster = ccluster,
      covs = ccovs,
      level = (1-p_value_cutoff)*100
  )
}
```


Generating different data sets:

```{r}
data_by <- data %>% filter(state == 9) %>% # Bavarian data only
  # Repeat (bandwidth) window calculation for data subsets
  mutate(
    closest = base::rank(abs(inhabs_rel_to_cutoff), ties.method = "last"),
    closest = closest/max(closest),
  )
```




# Introduction

Main specification & specification for Bavaria (since some of the data are available for Bavaria only):

```{r}
df <- data %>%
  select(ln_gross_expenditure_pc, total_seats, inhabs_rel_to_cutoff, above_cutoff, inhabitants_treshold_factor, inhabitants_treshold, year, ags, election_year, state, closest, clean_disc_acc_Höhmann, clean_disc_acc_to_my_research) %>%
  drop_na(ln_gross_expenditure_pc, total_seats, inhabs_rel_to_cutoff)
rdd <-
  rdrobust::rdrobust(
    y = df$ln_gross_expenditure_pc,
    x = df$inhabs_rel_to_cutoff,
    fuzzy = df$total_seats,
    cluster = df$inhabitants_treshold_factor,
    covs = model.matrix( ~ df$inhabitants_treshold_factor + df$year + df$state)
  )
summary(rdd)
df <- df %>% filter(state == 9)
rdd <-
  rdrobust::rdrobust(
    y = df$ln_gross_expenditure_pc,
    x = df$inhabs_rel_to_cutoff,
    fuzzy = df$total_seats,
    cluster = df$inhabitants_treshold_factor,
    covs = model.matrix( ~ df$inhabitants_treshold_factor + df$year)
  )
summary(rdd)
rm(df, rdd)
```

Unfortunately (for the argumentation), the "Law of 1/n" effect is significantly negative in Bavaria: At the threshold, spending decreases by 2.7 %, significant at $\alpha$ = 0.01.

General remark: I know that lots of the code used here may be improved by wrapper functions and functional programming. However, time constraints led me in some cases to look for the fastest (not the nicest) code idea available.








# Financing the "Law of 1/n"

On to the financing side of the "Law of 1/n"...

Write wrapper function to run `rdrobust` FE RDD model without covariates:

```{r, eval=FALSE}
# Not used due to issues with returning values
rdd_bi_fe_model <- function(...) {
  df <- data %>%
    select(..., inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, year, state) %>%
    drop_na()
  rdd <-
    rdrobust::rdrobust(
      y = df %>% pull(y),
      x = df$inhabs_rel_to_cutoff,
      fuzzy = df$total_seats,
      cluster = df$inhabitants_treshold_factor,
      covs = model.matrix( ~ df$inhabitants_treshold_factor + df$year + df$state)
      )
  summary(rdd)
  # out$call <- match.call()
  # class(out) <- "rdrobust"
  # return(out)
}
```

## H2: How is the additional spending financed?

The `gross revenue` variable is coded similarly to the `gross expenditure` variable: In natural logs and per capita.

Taxes at the cutoff:

```{r}
df <- data %>%
  select(ln_gross_revenue_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, year, state) %>%
  drop_na()
rdd_h2_taxes <-
  rdrobust::rdrobust(
    y = df$ln_gross_revenue_pc,
    x = df$inhabs_rel_to_cutoff,
    fuzzy = df$total_seats,
    cluster = df$inhabitants_treshold_factor,
    covs = model.matrix( ~ df$inhabitants_treshold_factor + df$year + df$state)
  )
summary(rdd_h2_taxes)
rm(df)
```

## H3: If taxes are used to fund the Law, which taxes?

Debt at the cutoff:

```{r}
df <- data %>%
  select(ln_net_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, year, state) %>%
  drop_na()
rdd_h3_debt <-
  rdrobust::rdrobust(
    y = df$ln_net_expenditure_pc,
    x = df$inhabs_rel_to_cutoff,
    fuzzy = df$total_seats,
    cluster = df$inhabitants_treshold_factor,
    covs = model.matrix( ~ df$inhabitants_treshold_factor + df$year + df$state)
  )
summary(rdd_h3_debt)
rm(df)
```

Note that the variable `net_expenditure` is apparently not equal to $gross\_revenue - gross\_expenditure$, correlation is only about 0.34.

## Export table:

```{r}
rdd_tex_export <- tibble(
  `Dependent variable:` = c("Model", "", "Council size", "", "", "Data sample", "Observations", "Bandwidth", "Observations below", "Observations above"),
  `Ln of gross revenue p. c.` = c("FE RDD w/o covariates", "(1)", paste0(round(rdd_h2_taxes$Estimate[1], round_decimals), assign_stars(rdd_h2_taxes$pv[3])), paste0("(", round(rdd_h2_taxes$se[1], round_decimals), ")"), paste0("[", round(rdd_h2_taxes$ci[3,1], 3), ", ", round(rdd_h2_taxes$ci[3,2], 3), "]"), "All data", sum(rdd_h2_taxes$N), round(rdd_h2_taxes$bws[1,1], round_decimals), rdd_h2_taxes$N_h[1], rdd_h2_taxes$N_h[2]),
  `Ln of net expenditure p. c.` = c("FE RDD w/o covariates", "(2)", paste0(round(rdd_h3_debt$Estimate[1], round_decimals), assign_stars(rdd_h3_debt$pv[3])), paste0("(", round(rdd_h3_debt$se[1], round_decimals), ")"), paste0("[", round(rdd_h3_debt$ci[3,1], 3), ", ", round(rdd_h3_debt$ci[3,2], 3), "]"), "All data", sum(rdd_h3_debt$N), round(rdd_h3_debt$bws[1,1], round_decimals), rdd_h3_debt$N_h[1], rdd_h3_debt$N_h[2])
  )
rdd_tex_export
```

```{r}
print(
  xtable::xtable(
    rdd_tex_export,
    align = "llcc"
    ),
  file = "tables/rdd_rdrobust_financing.tex",
  booktabs = TRUE,
  floating = FALSE,
  hline.after = c(-1, -1, 2, 5, nrow(rdd_tex_export), nrow(rdd_tex_export)),
  include.rownames = FALSE
)
```
```{r}
rm(rdd_tex_export)
```

## Digression: All revenue categories

Run regressions over all revenue categories:

```{r, eval=FALSE}
# to do: remove eval=FALSE
rev_category <- data %>%
  select(contains("revenue")) %>% # select expenditure categories
  names() # pull their names
rdd_vary_rev_category <- # prepare data set to store the results
  tibble(rev_category = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(2:last_col(), as.numeric))
for (i in rev_category) {
  df <- data %>%
    select((!!rlang::sym(i)), inhabs_rel_to_cutoff, total_seats,
           inhabitants_treshold_factor, year, state) %>%
    drop_na()
  rdd <-
    rdrobust::rdrobust(
      y = df %>% pull(i),
      x = df$inhabs_rel_to_cutoff,
      fuzzy = df$total_seats,
      cluster = df$inhabitants_treshold_factor,
      covs = model.matrix(~ df$inhabitants_treshold_factor + df$year + df$state)
    )
  #summary(rdd)
  rdd_vary_rev_category <- rdd_vary_rev_category %>%
    dplyr::add_row(
      rev_category = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_rev_category <- rdd_vary_rev_category %>%
  drop_na() %>%
  mutate(
    rev_category2 = c(
      "gross revenue",
      "administrative", "administrative: taxes",
      "administrative: transfers", "administrative: charges & fees",
      "capital", "capital: charges",
      "capital: allocations", "capital: loans",
      "tax: property tax A revenue", "tax: property tax B revenue",
      "tax: business tax", "tax: business tax revenue transfers",
      "tax: business tax revenue net", "tax: wage & income tax"
    )
  )
save(rdd_vary_rev_category, file = "tables_robustness_checks/rdd_vary_rev_category.Rdata")
rm(df)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_rev_category.Rdata")
rdd_vary_rev_category
```

```{r}
ggplot2::ggplot(data = rdd_vary_rev_category, aes(x = rev_category2, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(rdd_vary_rev_category$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(rdd_vary_rev_category$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(rdd_vary_rev_category$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  aes(stringr::str_wrap(rev_category2, 15)) +
  labs(x = NULL, y = "Increase in spending at the threshold") +
  coord_flip()
ggsave(filename = "plots/rdd_rev_categories.pdf", width = 6, height = 6*9/16)
```

Some suspiciously positive effects for variables related with the local business tax (but probably variables are highly correlated).

IV approach:

```{r}
df <- data %>%
  filter(closest <= 0.1)
rdd <- fixest::feols(c(ln_gross_revenue_pc, ln_revenue_administrative_pc,
                       ln_revenue_admin_taxes_pc, ln_revenue_admin_transfers_pc,
                       ln_revenue_admin_chargesfees_pc, ln_revenue_capital_pc,
                       ln_revenue_capital_charges_pc, ln_revenue_capital_allocations_pc,
                       ln_revenue_capital_loans_pc, ln_tax_prop_a_revenue_pc,
                       ln_tax_prop_b_revenue_pc, ln_tax_business_revenue_pc,
                       ln_tax_business_revenue_transfers_pc, ln_tax_business_revenue_net_pc,
                       ln_wage__income_tax_revenue_pc) ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats ~ # Instrument our standard RDD...
                       inhabs_rel_to_cutoff*above_cutoff, # ... with being above the cutoff
                     vcov = "threeway",
                     data = df)
summary(rdd)
```
```{r}
rm(df, rev_category)
```

Similar conclusions: No effect is singificant at commonly used significance levels, lowest p value: 0.2.



# Testing the Hsu & Shen (2019) heterogeneity test for `inhabitants_treshold`

Functions retrieved from the [authors dropbox](https://www.dropbox.com/sh/hacenzqpop3o15s/AAA-vdgQtgxwkBbundCkL_0Sa) (Hsu & Shen, 2019).

```{r, hs_load functions}
## load in robust bandwidth selection functions from CCT(2014)## 
#source("functions/Hsu_Shen_functions/rdbwselect.R")
#source("functions/Hsu_Shen_functions/functions.R")
# load in RD test functions
source("functions/Hsu_Shen_functions/RDHetero_Functions.R")
```

Choose general parameters (for details, see paper):

```{r}
#nwgrid <- 30
#nbs <- 1000 # = number of bootstraps?
smooth <- 4.5
```

```{r}
sh_test_df <-
  tibble(regression = "", data_set = "", H0 = "", p = "", bw = "") %>%
  mutate(across(4:last_col(), as.numeric)) %>%
  drop_na
```


Second-stage test (neither reduced-form nor first stage):

```{r, hus_shen_test}
df <- data %>% # prepare data set used for analysis
  select(
    ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats,
    inhabitants_treshold, state, year,
    inh_tot, pop_over65, unempl_rate, total_area_ha
    ) %>%
  drop_na()
y <- df %>% pull(ln_gross_expenditure_pc)
x <- df %>% pull(inhabs_rel_to_cutoff)
t <- df %>% pull(total_seats)
w <- df %>% pull(inhabitants_treshold)
n <- length(y)
mrdbw.out <- rdbwselect(y, x, fuzzy = t) # Use standard bw selector, not the IK one as in the paper
bw <- mrdbw.out$bws[1,1]*n^(1/5-1/smooth)
set.seed(123) # to do: remove
results<-RDHeteroTest(y=y,x=x,w=w,bw=bw,t=t)#,nwgrid=nwgrid,nbs=nbs)
# Save results in df
## Generate p values
bscdf_neg <- ecdf(results$stat_neg_bs)
bscdf_pos <- ecdf(results$stat_pos_bs)
bscdf_hetero <- ecdf(results$stat_hetero_bs)
sh_test_df <- sh_test_df %>%
    dplyr::add_row(
      regression = "Full",
      data_set = "All available",
      H0 = c("Uniformly Nonpositive Effect", "Uniformly Nonnegative Effect", "Homogeneous Effect"),
      p = c(1-bscdf_neg(results$stat_neg),
            bscdf_pos(results$stat_pos),
            1-bscdf_hetero(results$stat_hetero)),
      bw = bw
  )
sh_test_df
save(sh_test_df, file = "tables_robustness_checks/hsu_shen_het_test.RData")
rm(df, y, x, t, w, n)
```
```{r}
load(file = "tables_robustness_checks/hsu_shen_het_test.RData")
sh_test_df
bscdf_neg=ecdf(results$stat_neg_bs)
plot(bscdf_neg, main="(d) H0: Uniformly Nonpositive Effect",xlab=paste("exam-takers, p-value=",as.character(format(1-bscdf_neg(results$stat_neg),sep=""),digits=2)),xlim=c(min(cbind(knots(bscdf_neg),results$stat_neg))-0.02,max(cbind(knots(bscdf_neg),results$stat_neg))+0.002),pch=20,cex.main=0.75)
lines(seq(0,1,0.001)*0+results$stat_neg,seq(0,1,0.001))
bscdf_pos=ecdf(results$stat_pos_bs)
plot(bscdf_pos, main="(e) H0: Uniformly Nonnegative Effect",xlab=paste("exam-takers, p-value=",as.character(format(bscdf_pos(results$stat_pos),sep=""),digits=2)),xlim=c(min(cbind(knots(bscdf_pos),results$stat_pos))-0.02,max(cbind(knots(bscdf_pos),results$stat_pos))+0.002),pch=20,cex.main=0.75)
lines(seq(0,1,0.001)*0+results$stat_pos,seq(0,1,0.001))
bscdf_hetero=ecdf(results$stat_hetero_bs)
plot(bscdf_hetero, main="(f) H0: Homogeneous Effect",xlab=paste("exam-takers, p-value=",as.character(format(1-bscdf_hetero(results$stat_hetero),sep=""),digits=2)),xlim=c(0,max(cbind(knots(bscdf_hetero),results$stat_hetero))+0.002),pch=20,cex.main=0.75)
lines(seq(0,1,0.001)*0+results$stat_hetero,seq(0,1,0.001))
```
```{r}
rm(results)
```


However, it appears to me that you cannot include covariates (i. e. fixed effects in this case), rendering the estimation obsolete.

In addition, test results change upon changing the (completely unrelelated) number of variables in the `select()` command above which is puzzling to me.

Reguly's (2021) code that tests for the exact variables causing the heterogeneity is unfortunately only available for Matlab.


# Variations over states and years

Variation of the "Law of 1/n" between years and states. There are two general methods to detect treatment heterogeneity: The subsample and the interaction methods. While the former can be run in `rdrobust` and hence, is more "state of the art", only the latter allows for inference, e. g. employing multiple testing.

## Years

Subsample method: 

```{r, year_variation, eval=FALSE}
# to do: remove eval=FALSE
data_year <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year) %>%
  drop_na()
all_years <- data_year %>% distinct(year) %>% pull() # vector of years
rdd_vary_year <- # prepare data set to store the results
  tibble(year = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(everything(), as.numeric))
for (i in all_years) {
  print(paste("year:", i))
  df <- data_year %>%
    filter(year == i)
  rdd <-
    rdrobust::rdrobust(
      y = df$ln_gross_expenditure_pc,
      x = df$inhabs_rel_to_cutoff,
      fuzzy = df$total_seats,
      cluster = df$inhabitants_treshold_factor,
      covs = model.matrix( ~ df$inhabitants_treshold_factor + df$state), # Dropping year FE, obviously
      level = (1-p_value_cutoff)*100
  )
  #summary(rdd)
  rdd_vary_year <- rdd_vary_year %>%
    dplyr::add_row(
      year = as.numeric(i),
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_year <- rdd_vary_year %>% drop_na()
save(rdd_vary_year, file = "tables_robustness_checks/rdd_vary_year.Rdata")
rm(all_years, data_year, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_year.Rdata")
rdd_vary_year
```

```{r, rdd_window_plot}
ggplot2::ggplot(data = rdd_vary_year, aes(x = year, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(rdd_vary_year$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(rdd_vary_year$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(rdd_vary_year$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Year", y = "Increase in spending at the threshold")
```

For each year: Not much variation in the results here (as expected).

Interaction-term method using the `rdrobust` package -- not possible as far as I know:

```{r, eval=FALSE}
df <- data %>%
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year) %>%
  drop_na()
rdd <- rdrobust::rdrobust(
      y = df$ln_gross_expenditure_pc,
      x = df$inhabs_rel_to_cutoff : model.matrix( ~ df$year),
      fuzzy = df$total_seats,
      cluster = df$inhabitants_treshold_factor,
      covs = model.matrix( ~ df$inhabitants_treshold_factor + df$state) # Dropping year FE, obviously
  )
summary(rdd)
rm(df)
```


Interaction-term method using an IV approach with `year` included as a factor, not as a numerical variable:

```{r}
df <- data %>%
  filter(closest <= 0.1)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats ~ # Instrument our standard RDD...
                       inhabs_rel_to_cutoff*above_cutoff, # ... with being above the cutoff
                     vcov = "threeway",
                     data = df)
summary(rdd)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*year ~ # Instrument our standard RDD...
                       inhabs_rel_to_cutoff*above_cutoff*year, # ... with being above the cutoff
                     vcov = "twoway",
                     data = df)
summary(rdd)
# joint test on interactions
fixest::wald(rdd, "fit_total_seats:year")
#rm(df)
```

The joint test confirms what we saw above: No deviations from baseline treatment effect in 2002.


## States

Subsample method, fuzzy RDD: 

```{r, state_variation_fuz, eval=FALSE}
# to do: remove eval=FALSE
data_state <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year) %>%
  drop_na()
all_states <- data_state %>% distinct(state) %>% filter(state != "15") %>% pull() # vector of states
rdd_vary_states <- # prepare data set to store the results
  tibble(state = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "",
         stage = "") %>%
  mutate(across(1:last_col(), as.numeric))
for (i in all_states) {
  print(paste("state:", i))
  df <- data_state %>%
    filter(state == i)
  rdd <-
    rdrobust::rdrobust(
      y = df$ln_gross_expenditure_pc,
      x = df$inhabs_rel_to_cutoff,
      fuzzy = df$total_seats,
      cluster = df$inhabitants_treshold_factor,
      covs = model.matrix( ~ df$inhabitants_treshold_factor + df$year), # Dropping state FE, obviously
      level = (1-p_value_cutoff)*100
  )
  #summary(rdd)
  rdd_vary_states <- rdd_vary_states %>%
    dplyr::add_row(
      state = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2],
      stage = 2
      ) %>%
    dplyr::add_row(
      state = i,
      point_estimate = rdd$tau_T[1],
      se = rdd$se_T[1],
      se_robust = rdd$se_T[3],
      ci_lower = rdd$ci_T[3,1],
      ci_upper = rdd$ci_T[3,2],
      p = rdd$pv_T[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2],
      stage = 1
    )
}
rdd_vary_states <- rdd_vary_states %>% drop_na() %>% mutate(method = "fuzzy")
save(rdd_vary_states, file = "tables_robustness_checks/rdd_vary_states.Rdata")
rm(all_states, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_states.Rdata")
# First stage:
rdd_vary_states %>% filter(stage == 1, method == "fuzzy")
# Second stage:
rdd_vary_states %>% filter(stage == 2, method == "fuzzy")
```

```{r}
# First stage
df <- rdd_vary_states %>%
  filter(state != 10, stage == 1) %>% # CIs too large
  mutate(state_name = case_when(
    state == 1 ~ "SH",
    state == 5 ~ "NW",
    state == 6 ~ "HE",
    state == 7 ~ "RP",
    state == 8 ~ "BW",
    state == 9 ~ "BY",
    state == 10 ~ "SL",
    state == 13 ~ "MV",
    state == 14 ~ "SN",
    state == 16 ~ "TH"
  ),
  state_name = fct_reorder(state_name, state)) %>%
  rowwise() %>%
  mutate(effective_n = paste0("n=", trimws(format(sum(obs_below, obs_above), big.mark = ",")))) %>%
  ungroup()
plot_states_fuzzy1 <- ggplot2::ggplot(data = df, aes(x = state_name, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_text(aes(y = -1.05, label = effective_n),
            colour = ifelse(df$p <= p_value_cutoff, 2, 1), vjust = 1) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  labs(title = "First stage", x = "State", y = "Increase in council size at the threshold")
plot_states_fuzzy1
ggsave(filename = "plots/rdd_states_fuzzy1.pdf", width = 6, height = 6*9/16)
# Second stage
df <- rdd_vary_states %>%
  filter(state != 14, stage == 2) %>% # CIs too large
  mutate(state_name = case_when(
    state == 1 ~ "SH",
    state == 5 ~ "NW",
    state == 6 ~ "HE",
    state == 7 ~ "RP",
    state == 8 ~ "BW",
    state == 9 ~ "BY",
    state == 10 ~ "SL",
    state == 13 ~ "MV",
    state == 16 ~ "TH"
  ),
  state_name = fct_reorder(state_name, state)) %>%
  rowwise() %>%
  mutate(effective_n = paste0("n=", trimws(format(sum(obs_below, obs_above), big.mark = ",")))) %>%
  ungroup()
plot_states_fuzzy2 <- ggplot2::ggplot(data = df, aes(x = state_name, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_text(aes(y = -0.165, label = effective_n),
            colour = ifelse(df$p <= p_value_cutoff, 2, 1), vjust = 1) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Second stage", x = "State", y = "Increase in spending at the threshold")
plot_states_fuzzy2
ggsave(filename = "plots/rdd_states_fuzzy2.pdf", width = 6, height = 6*9/16)
rm(df)
```

First stage: State 10 removed due to large confidence bands.

Second stage: State 14's (SN) CIs are too large, state `15` produces an error. Hence, both are excluded.


Subsample method, sharp approach (only possible for a subset of states):

```{r, state_variation_shp, eval=FALSE}
# to do: remove eval=FALSE
# data_state <- data %>% # prepare data set used for analysis
#   select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year) %>%
#   drop_na()
all_states <- data_state %>% distinct(state) %>% filter(state %in% c(7, 9, 10, 16)) %>% pull() # vector of states
# rdd_vary_states <- # prepare data set to store the results
#   tibble(state = "", point_estimate = "", se = "", se_robust = "",
#          ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "",
#          stage = "") %>%
#   mutate(across(1:last_col(), as.numeric))
for (i in all_states) {
  print(paste("state:", i))
  df <- data_state %>%
    filter(state == i)
  rdd <-
    rdrobust::rdrobust(
      y = df$ln_gross_expenditure_pc,
      x = df$inhabs_rel_to_cutoff,
      cluster = df$inhabitants_treshold_factor,
      covs = model.matrix( ~ df$inhabitants_treshold_factor + df$year), # Dropping state FE, obviously
      level = (1-p_value_cutoff)*100
  )
  #summary(rdd)
  rdd_vary_states <- rdd_vary_states %>%
    dplyr::add_row(
      state = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2],
      method = "sharp"
      )
}
rdd_vary_states <- rdd_vary_states %>% drop_na(state)
save(rdd_vary_states, file = "tables_robustness_checks/rdd_vary_states.Rdata")
rm(all_states, data_state, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_states.Rdata")
rdd_vary_states %>% filter(method == "sharp")
```

```{r}
# Second stage
df <- rdd_vary_states %>%
  filter(method == "sharp") %>% # CIs too large
  mutate(state_name = case_when(
    state == 7 ~ "RP",
    state == 9 ~ "BY",
    state == 10 ~ "SL",
    state == 16 ~ "TH"
  ),
  state_name = fct_reorder(state_name, state)) %>%
  rowwise() %>%
  mutate(effective_n = paste0("n=", trimws(format(sum(obs_below, obs_above), big.mark = ",")))) %>%
  ungroup()
plot_states_sharp <- ggplot2::ggplot(data = df, aes(x = state_name, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_text(aes(y = -0.09, label = effective_n),
            colour = ifelse(df$p <= p_value_cutoff, 2, 1), vjust = 1) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "State", y = "Increase in spending at the threshold")
plot_states_sharp
ggsave(filename = "plots/rdd_states_sharp.pdf", width = 6, height = 6*9/16)
rm(df)
```

Plot `rdrobust` results in one:
```{r, eval=FALSE}
# to do: delete code
plot_states <- ggpubr::ggarrange(
  plot_states_fuzzy1, plot_states_fuzzy2, plot_states_sharp,
  # labels = c("SH", "NW", "Hesse", "Rhineland-Palatinate", "Baden-Württemberg",
  #            "Bavaria", "Saarland", "Mecklenburg-Vorpommern", "Saxony", "Thuringia"),
  #labels = paste(" ", c("SH", "NW", "HE", "RP", "BW", "BY", "SL", "MV", "SN", "TH")),
  #label.x = "Population",
  #label.y = "Council size",
  #common.legend = TRUE,
  ncol = 2, nrow = 2) %>%
  annotate_figure(
    # See https://github.com/kassambara/ggpubr/issues/78
    #left = text_grob("Council size", rot = 90),
    #bottom = text_grob("Population")
)
plot_states
```

Some notes:

```{r}
# Saxony (SN): municipalities with < 10000 inhabs
nrow(data %>% filter(state == 14))
nrow(data %>% filter(state == 14, exact_pop <= 10000))
nrow(data %>% filter(state == 14, exact_pop <= 10000)) / nrow(data %>% filter(state == 14))
# Saarland (SL):
nrow(data %>% filter(state == 10))
```



Interaction-term method using an IV approach:

```{r}
df <- data %>%
  filter(closest <= 0.1) %>%
  mutate(state = as.factor(state)) # to do: why isn't it in `data`
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*state ~ # Instrument our standard RDD...
                       inhabs_rel_to_cutoff*above_cutoff*state, # ... with being above the cutoff
                     vcov = "twoway",
                     data = df)
summary(rdd)
# joint test on interactions
fixest::wald(rdd, "fit_total_seats:state")
rm(df)
```

Test more extreme "individual" values:

```{r}
df <- data %>%
  filter(closest <= 0.1) %>%
  mutate(state = relevel(as.factor(state), ref = "10")) # to do: why isn't it in `data`
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*state ~ # Instrument our standard RDD...
                       inhabs_rel_to_cutoff*above_cutoff*state, # ... with being above the cutoff
                     vcov = "twoway",
                     data = df)
summary(rdd)
# joint test on interactions
fixest::wald(rdd, "fit_total_seats:state")
rm(df)
```
```{r}
df <- data %>%
  filter(closest <= 0.1) %>%
  mutate(state = relevel(as.factor(state), ref = "13")) # to do: why isn't it in `data`
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*state ~ # Instrument our standard RDD...
                       inhabs_rel_to_cutoff*above_cutoff*state, # ... with being above the cutoff
                     vcov = "twoway",
                     data = df)
summary(rdd)
# joint test on interactions
fixest::wald(rdd, "fit_total_seats:state")
rm(df)
```

States 13 (MV) and 15 (SA) apparently not testable...

To conclude: very contradicting results. Subsample yields several differences between states, interaction shows no significant results




Run RDD for Bavaria as some data are only available for Bavaria

# Different political systems

## H4: Bureaucracy-council agency conflict

## H5: At-large vs. ward electoral systems

Dummy `ward_elections` is 1 for states 01 and 05, 0 otherwise. 01 & 05 have 

Subsample method:

```{r, rdrobust_ward, eval=FALSE}
# to do: remove eval=FALSE
data_subset <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year, ward_elections) %>%
  drop_na()
all_values <- data_subset %>% distinct(ward_elections) %>% pull() # vector of values
rdd_vary_ward <- # prepare data set to store the results
  tibble(value = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(everything(), as.numeric))
for (i in all_values) {
  print(paste("ward (0 is at large, 1 is partly in wards):", i))
  df <- data_subset %>%
    filter(ward_elections == i)
  rdd <-
    rdrobust_wrapper(
      ccluster = df$inhabitants_treshold_factor,
      ccovs = model.matrix( ~ df$inhabitants_treshold_factor + df$year + df$state) # Dropping year FE
      )
  #summary(rdd)
  rdd_vary_ward <- rdd_vary_ward %>%
    dplyr::add_row(
      value = as.numeric(i),
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_ward <- rdd_vary_ward %>% drop_na()
save(rdd_vary_ward, file = "tables_robustness_checks/rdd_vary_ward.Rdata")
rm(all_values, data_subset, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_ward.Rdata")
rdd_vary_ward
```

```{r}
ggplot2::ggplot(data = rdd_vary_ward, aes(x = value, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(rdd_vary_ward$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(rdd_vary_ward$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(rdd_vary_ward$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Increase in spending at the threshold")
```

Preliminary evidence looks promising: SH and NW spend more at the threshold (about 1.9 %), likely primarily driven by NW (see states section).


Interaction-term method using an IV approach::

```{r, eval=FALSE}
df <- data %>%
  filter(closest <= 0.1) %>%
  mutate(ward_elections = as.factor(ward_elections))
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*ward_elections ~
                       inhabs_rel_to_cutoff*above_cutoff*ward_elections,
                     vcov = "threeway",
                     data = df)
summary(rdd)
#rm(df)
```

However in the parametric approach, nothing proves significant, in line with what one might expect based on the overlapping CIs in the plot above.


## H6: Role of the mayor

How to define role of mayor? How to define `const_typ_sueddt`?

Subsample method:

```{r, eval=FALSE}
# to do: remove eval=FALSE
data_subset <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year, const_typ_sueddt) %>%
  drop_na()
all_values <- data_subset %>% distinct(const_typ_sueddt) %>% pull() # vector of values
rdd_vary_const_type <- # prepare data set to store the results
  tibble(const_typ_sueddt = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(everything(), as.numeric))
for (i in all_values) {
  print(paste("constitutional type:", i))
  df <- data_subset %>%
    filter(const_typ_sueddt == i)
  rdd <-
    rdrobust_wrapper(
      ccluster = df$inhabitants_treshold_factor,
      ccovs = model.matrix( ~ df$inhabitants_treshold_factor + df$state + df$year) # FE
  )
  #summary(rdd)
  rdd_vary_const_type <- rdd_vary_const_type %>%
    dplyr::add_row(
      const_typ_sueddt = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_const_type <- rdd_vary_const_type %>% drop_na()
save(rdd_vary_const_type, file = "tables_robustness_checks/rdd_vary_const_type.Rdata")
rm(all_values, data_subset, df, i, rdd)
```
```{r, eval=FALSE}
load(file = "tables_robustness_checks/rdd_vary_const_type.Rdata")
rdd_vary_const_type
```

```{r, eval=FALSE}
ggplot2::ggplot(data = rdd_vary_const_type, aes(x = const_typ_sueddt, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(rdd_vary_const_type$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(rdd_vary_const_type$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(rdd_vary_const_type$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Increase in spending at the threshold")
```

No differences visible.


Interaction-term method using an IV approach:

```{r, eval=FALSE}
df <- data %>%
  filter(closest <= 0.1)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*const_typ_sueddt ~
                       inhabs_rel_to_cutoff*above_cutoff*const_typ_sueddt,
                     vcov = "threeway",
                     data = df)
summary(rdd)
rm(df)
```

Local constititutional type does not matter.


## H7: Mayoral party affiliation

Bavarian data only!

Subsample method:

```{r}
data_subset <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year, ends_with("mayor"), closest, above_cutoff) %>%
  mutate(mayor_party_affiliation = case_when(
    cdu_csu_mayor == 0 & spd_mayor == 0 ~ "others",
    cdu_csu_mayor == 1 ~ "cdu_csu",
    spd_mayor == 1 ~ "spd"
  )) %>%
  drop_na()
table(data_subset$mayor_party_affiliation)
```
```{r, rdrobust_mayor_party, eval=FALSE}
# to do: remove eval=FALSE
all_values <- data_subset %>% distinct(mayor_party_affiliation) %>% pull() # vector of values
rdd_vary_may_affil <- # prepare data set to store the results
  tibble(mayor_party_affiliation = "", method = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(3:last_col(), as.numeric))
for (i in all_values) {
  print(paste("Mayoral party affiliation:", i))
  df <- data_subset %>%
    filter(mayor_party_affiliation == i)
  print("fuzzy")
  rdd <-
    rdrobust_wrapper(
      ccluster = df$inhabitants_treshold_factor,
      ccovs = model.matrix( ~ df$inhabitants_treshold_factor + df$year) # Dropping year FE, obviously
  )
  rdd_vary_may_affil <- rdd_vary_may_affil %>%
    dplyr::add_row(
      mayor_party_affiliation = i,
      method = "fuzzy",
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
  print("sharp")
  rdd <-
    rdrobust::rdrobust(
      y = df$ln_gross_expenditure_pc,
      x = df$inhabs_rel_to_cutoff,
      #fuzzy = df$total_seats,
      cluster = df$inhabitants_treshold_factor,
      covs = model.matrix( ~ df$inhabitants_treshold_factor + df$year), # Dropping year FE, obviously
      level = (1-p_value_cutoff)*100
  )
  rdd_vary_may_affil <- rdd_vary_may_affil %>%
    dplyr::add_row(
      mayor_party_affiliation = i,
      method = "sharp",
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_may_affil <- rdd_vary_may_affil %>%
  mutate(mayor_party_affiliation = case_when(
    mayor_party_affiliation == "cdu_csu" ~ "CDU/CSU",
    mayor_party_affiliation == "others" ~ "Others",
    mayor_party_affiliation == "spd" ~ "SPD"
  )) %>%
  drop_na()
save(rdd_vary_may_affil, file = "tables_robustness_checks/rdd_vary_may_affil.Rdata")
rm(all_values, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_may_affil.Rdata")
rdd_vary_may_affil
```

```{r}
for (i in c("fuzzy", "sharp")) {
  df <- rdd_vary_may_affil %>%
    filter(method == i) %>%
    rowwise() %>%
    mutate(effective_n = paste0("n=", trimws(format(sum(obs_below, obs_above), big.mark = ",")))) %>%
    ungroup()
  p <- ggplot2::ggplot(data = df, aes(x = reorder(mayor_party_affiliation, c(1,3,2)),
                                      y = point_estimate)) +
    geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                  color = ifelse(df$p <= p_value_cutoff, 2, 1),
                  linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                  width = 0.5) +
    geom_text(aes(y = -0.135, label = effective_n),
            colour = ifelse(df$p <= p_value_cutoff, 2, 1), vjust = 1) +
    geom_hline(aes(yintercept = 0), linetype = "dotted") +
    scale_y_continuous(labels = scales::percent) +
    labs(y = "Increase in spending at the threshold", title = i)
  print(p)
}
# Make plot "publication-ready":
p <- p +
  labs(x = NULL, title = NULL)
ggsave(filename = "plots/rdd_mayor_affiliation.pdf", plot = p, width = 6, height = 6*9/16)
rm(df, p)
```

Negative "Law of 1/n" effect found for Bavaria mainly driven by both CSU and SPD mayors. Mind the heterogeneity of the others category.


Interaction-term method in sharp approach:

```{r}
df <- data_subset %>% # Use data set from above
  filter(closest <= 0.1)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       inhabs_rel_to_cutoff*above_cutoff*mayor_party_affiliation |
                       inhabitants_treshold_factor + year, # fixed-effect controls
                     vcov = "twoway",
                     data = df)
summary(rdd)
# joint test on interactions
fixest::wald(rdd, "above_cutoff:mayor_party_affiliation")
```

Interaction-term method using an IV approach (fuzzy):

```{r}
df <- data_subset %>% # Use data set from above
  filter(closest <= 0.1)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*mayor_party_affiliation ~
                       inhabs_rel_to_cutoff*above_cutoff*mayor_party_affiliation,
                     vcov = "twoway",
                     data = df)
summary(rdd)
# joint test on interactions
fixest::wald(rdd, "fit_total_seats:mayor_party_affiliation")
```
```{r}
rm(df, data_subset)
```

The baseline effect for CSU mayors is -2.1 % (nonsignificant). The "individual" effects for others and SPD are not significantly different from zero either (SPD only at 10 %, others not at all). However, the joint significance test for differences from CSU mayors is significant at p = 0.05. Both SPD and other mayors seem to drive the effect up.



## H8: Parties in parliament

Number of parties in parliament is presumably biased downwards -- Number of parties in parliament (biased downwards b/c of aggregates (others, waehlergruppen)!)

More sophisticated analysis is possible by weighting the number of parties in parliament, e. g. Herfindahl index.

Data available for the following states:
`r data %>% filter(!is.na(no_parties_in_parliament)) %>% group_by(state) %>% summarize() %>% pull(state) %>% paste(., collapse = ",")`

### `number_of_parties` in parliament variable

Subsample method:

```{r}
data_subset <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year, no_parties_in_parliament) %>%
  drop_na()
table(data_subset$state)
```
```{r, eval=FALSE}
# to do: remove eval=FALSE
all_values <- data_subset %>%
  arrange(no_parties_in_parliament) %>%
  filter(no_parties_in_parliament <= 7) %>%
  distinct(no_parties_in_parliament) %>%
  pull() # vector of values
rdd_vary_no_of_part <- # prepare data set to store the results
  tibble(no_parties_in_parliament = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(everything(), as.numeric))
for (i in all_values) {
  print(paste("no_parties_in_parliament:", i))
  df <- data_subset %>%
    filter(no_parties_in_parliament == i)
  rdd <-
    rdrobust_wrapper(
      ccluster = df$inhabitants_treshold_factor,
      ccovs = model.matrix( ~ df$inhabitants_treshold_factor + df$state + df$year) # FE
  )
  #summary(rdd)
  rdd_vary_no_of_part <- rdd_vary_no_of_part %>%
    dplyr::add_row(
      no_parties_in_parliament = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_no_of_part <- rdd_vary_no_of_part %>% drop_na()
save(rdd_vary_no_of_part, file = "tables_robustness_checks/rdd_vary_no_of_part.Rdata")
rm(all_values, data_subset, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_no_of_part.Rdata")
rdd_vary_no_of_part
```

```{r}
df <- rdd_vary_no_of_part %>%
  rowwise() %>%
  mutate(effective_n = paste0("n=", trimws(format(sum(obs_below, obs_above), big.mark = ",")))) %>%
  ungroup()
ggplot2::ggplot(data = df, aes(x = no_parties_in_parliament, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_text(aes(y = -0.09, label = effective_n),
            colour = ifelse(df$p <= p_value_cutoff, 2, 1), vjust = 1) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Number of parties in parliament (unweighted)",
       y = "Increase in spending at the threshold")
rm(df)
```

To me, it does not look like there is much treatment effect variation.

Interaction-term method using an IV approach:

```{r}
df <- data %>%
  filter(closest <= 0.1) %>%
  mutate(no_parties_in_parliament2 = as.factor(no_parties_in_parliament))
# no_parties_in_parliament categorically
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*no_parties_in_parliament2 ~
                       inhabs_rel_to_cutoff*above_cutoff*no_parties_in_parliament2,
                     vcov = "threeway",
                     data = df)
summary(rdd)
# joint test on interactions
fixest::wald(rdd, "fit_total_seats:no_parties_in_parliament2")
# no_parties_in_parliament continuously
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*no_parties_in_parliament ~
                       inhabs_rel_to_cutoff*above_cutoff*no_parties_in_parliament,
                     vcov = "threeway",
                     data = df)
summary(rdd)
rm(df)
```

Treatment effect ("Law of 1/n") does not vary in the number of parties in parliament.

### HHI

Subsample method:

```{r, eval=FALSE}
# to do: remove eval=FALSE
data_subset <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year, parties_in_parliament_hhi) %>%
  mutate(parties_in_parliament_hhi_quant = cut(
    parties_in_parliament_hhi,
    breaks = c(quantile(parties_in_parliament_hhi, seq(0, 1, 0.25), na.rm = TRUE))
    )) %>%
  drop_na()
all_values <- data_subset %>% distinct(parties_in_parliament_hhi_quant) %>% pull() # vector of values
rdd_vary_no_of_part2 <- # prepare data set to store the results
  tibble(parties_in_parliament_hhi_quant = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(2:last_col(), as.numeric))
for (i in all_values) {
  print(paste("parties_in_parliament_hhi_quant:", i))
  df <- data_subset %>%
    filter(parties_in_parliament_hhi_quant == i)
  rdd <-
    rdrobust_wrapper(
      ccluster = df$inhabitants_treshold_factor,
      ccovs = model.matrix( ~ df$inhabitants_treshold_factor + df$state + df$year) # FE
  )
  #summary(rdd)
  rdd_vary_no_of_part2 <- rdd_vary_no_of_part2 %>%
    dplyr::add_row(
      parties_in_parliament_hhi_quant = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_no_of_part2 <- rdd_vary_no_of_part2 %>% drop_na()
save(rdd_vary_no_of_part2, file = "tables_robustness_checks/rdd_vary_no_of_part2.Rdata")
rm(all_values, data_subset, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_no_of_part2.Rdata")
rdd_vary_no_of_part2
```

```{r}
df <- rdd_vary_no_of_part2 %>%
  rowwise() %>%
  mutate(effective_n = paste0("n=", trimws(format(sum(obs_below, obs_above), big.mark = ",")))) %>%
  ungroup()
ggplot2::ggplot(data = df, aes(x = parties_in_parliament_hhi_quant, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_text(aes(y = -0.09, label = effective_n),
            colour = ifelse(df$p <= p_value_cutoff, 2, 1), vjust = 1) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Number of parties in parliament by HHI",
       y = "Increase in spending at the threshold")
rm(df)
```

Similar to the previous `no_parties_in_parliament` result: No effect variation here.

Interaction-term method using an IV approach:

```{r}
df <- data %>%
  filter(closest <= 0.1)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*parties_in_parliament_hhi ~
                       inhabs_rel_to_cutoff*above_cutoff*parties_in_parliament_hhi,
                     vcov = "threeway",
                     data = df)
summary(rdd)
rm(df)
```

This completes the picture: No treatment effect variation here.


## H9: Absolute majority in parliament

Data available for the following states:
`r data %>% filter(!is.na(absolute_majority)) %>% group_by(state) %>% summarize() %>% pull(state) %>% paste(., collapse = ",")`

Subsample method:

```{r}
data_subset <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year, absolute_majority) %>%
  drop_na()
table(data_subset$state)
lims <- c(-0.0425, 0.04) # ggplot y axis limits
```
```{r, eval=FALSE}
# to do: remove eval=FALSE
all_values <- data_subset %>% distinct(absolute_majority) %>% pull() # vector of values
rdd_vary_abs_majority <- # prepare data set to store the results
  tibble(absolute_majority = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(everything(), as.numeric))
for (i in all_values) {
  print(paste("absolute_majority:", i))
  df <- data_subset %>%
    filter(absolute_majority == i)
  rdd <-
    rdrobust_wrapper(
      ccluster = df$inhabitants_treshold_factor,
      ccovs = model.matrix( ~ df$inhabitants_treshold_factor + df$state + df$year) # FE
  )
  #summary(rdd)
  rdd_vary_abs_majority <- rdd_vary_abs_majority %>%
    dplyr::add_row(
      absolute_majority = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_abs_majority <- rdd_vary_abs_majority %>% drop_na()
save(rdd_vary_abs_majority, file = "tables_robustness_checks/rdd_vary_abs_majority1.Rdata")
rm(all_values, data_subset, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_abs_majority1.Rdata")
rdd_vary_abs_majority
```

```{r}
df <- rdd_vary_abs_majority %>%
  mutate(absolute_majority = as.factor(absolute_majority),
         absolute_majority = case_when(
           absolute_majority == 1 ~ "Abs. majority by single party",
           absolute_majority == 0 ~ "No abs. majority by single party"
         )) %>%
  rowwise() %>%
  mutate(note = paste0(
    "n=",
    trimws(format(sum(obs_below, obs_above), big.mark = ",")),
    "\np=",
    round(p, 2)
    )) %>% 
  ungroup()
p_maj1 <-
  ggplot2::ggplot(data = df, aes(x = absolute_majority, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  geom_text(aes(y = -0.04, label = note),
            colour = ifelse(df$p <= p_value_cutoff, 2, 1), vjust = 0) +
  scale_y_continuous(limits = lims, labels = scales::percent) +
  aes(stringr::str_wrap(absolute_majority, 15)) +
  labs(x = NULL, y = "Increase in spending at the threshold")
p_maj1
# Adjustments for "publication"
p_maj1 <- p_maj1 + labs(title = "Absolute majority", y = NULL)
rm(df)
```

No differences.


Interaction-term method using an IV approach:

```{r}
df <- data %>%
  filter(closest <= 0.1)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*absolute_majority ~
                       inhabs_rel_to_cutoff*above_cutoff*absolute_majority,
                     vcov = "threeway",
                     data = df)
summary(rdd)
#rm(df)
```

This squares nicely with the `rdrobust` results: No differences.


## H10: Party affiliation of (absolute) majority party

Why only looking at *absolute* majorities? Easier to identify effect, e. g. `cdu_csu` might sit at 40 % of council seats but `spd` and greens might jointly be at 60 %. Hence, the left-wing party would have a majority over the conservatives but the data set might lead us to think that `cdu_csu` "dictates" policies.

### Overall data set

Subsample method:

```{r}
data_subset <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year, absolute_majority, cdu_csu_majority, spd_majority, waehlergruppen_majority, closest, above_cutoff) %>%
  mutate(abs_majority_party = case_when(
    cdu_csu_majority == 1 ~ "CDU/CSU abs. majority",
    spd_majority == 1 ~ "Non CDU/CSU abs. majority", # spd only yields error in rdrobust...
    #waehlergruppen_majority == 1 ~ "waehlergruppen",
    waehlergruppen_majority == 1 ~ "Non CDU/CSU abs. majority",
    absolute_majority == 0 ~ "No abs. majority"
  )) %>%
  select(-c(cdu_csu_majority, spd_majority, waehlergruppen_majority, absolute_majority)) %>%
  drop_na()
table(data_subset$state)
```
```{r, eval=FALSE}
# to do: remove eval=FALSE
all_values <- data_subset %>% distinct(abs_majority_party) %>% pull() # vector of values
rdd_vary_abs_majority2 <- # prepare data set to store the results
  tibble(abs_majority_party = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(2:last_col(), as.numeric))
for (i in all_values) {
  print(paste("abs_majority_party:", i))
  df <- data_subset %>%
    filter(abs_majority_party == i)
  rdd <-
    rdrobust_wrapper(
      ccluster = df$inhabitants_treshold_factor,
      ccovs = model.matrix( ~ df$inhabitants_treshold_factor + df$state + df$year) # FE
  )
  #summary(rdd)
  rdd_vary_abs_majority2 <- rdd_vary_abs_majority2 %>%
    dplyr::add_row(
      abs_majority_party = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_abs_majority2 <- rdd_vary_abs_majority2 %>% drop_na()
save(rdd_vary_abs_majority2, file = "tables_robustness_checks/rdd_vary_abs_majority2.Rdata")
rm(all_values, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_abs_majority2.Rdata")
rdd_vary_abs_majority2
```

```{r}
df <- rdd_vary_abs_majority2 %>%
  mutate(
    abs_majority_party = stringr::str_wrap(abs_majority_party, 15),
    abs_majority_party = fct_reorder(abs_majority_party, c(3, 1, 2))
    ) %>%
  rowwise() %>%
  mutate(note = paste0(
    "n=",
    trimws(format(sum(obs_below, obs_above), big.mark = ",")),
    "\np=",
    round(p, 2)
    )) %>% 
  ungroup()
p_maj2 <-
  ggplot2::ggplot(data = df, aes(x = abs_majority_party, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_text(aes(y = -0.04, label = note),
            colour = ifelse(df$p <= p_value_cutoff, 2, 1), vjust = 0) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(limits = lims, labels = scales::percent) +
  #aes(stringr::str_wrap(abs_majority_party, 15)) +
  labs(x = NULL, y = "Increase in spending at the threshold")
p_maj2
p_maj2 <- p_maj2 + labs(title = "Absolute majority by party", y = NULL)
#rm(df)
```

No effect visible here. `spd` is not a separate category as it would yield an error, potentially owing to too few observations.

Interaction-term method using an IV approach:

```{r}
df <- data_subset %>%
  filter(closest <= 0.1) #%>%
  # mutate(abs_majority_party = case_when(
  #   cdu_csu_majority == 1 ~ "cdu_csu",
  #   spd_majority == 1 ~ , # spd only yields error in rdrobust...
  #   #waehlergruppen_majority == 1 ~ "waehlergruppen",
  #   TRUE ~ "neither cdu_csu nor spd"
  # ))
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*abs_majority_party ~
                       inhabs_rel_to_cutoff*above_cutoff*abs_majority_party,
                     vcov = "threeway",
                     data = df)
summary(rdd)
# joint test on interactions
fixest::wald(rdd, "fit_total_seats:abs_majority_party")
```
```{r}
rm(df)
```

Yup, no effect visible here, as indicated by the `rdrobust` results.

### Bavaria

```{r}
data_subset <- data_by %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year, cdu_csu_majority, spd_majority, waehlergruppen_majority, closest, above_cutoff) %>%
  mutate(abs_majority_party = case_when(
    cdu_csu_majority == 1 ~ "cdu_csu",
    spd_majority == 1 ~ "neither cdu_csu nor waehlergruppen", # spd only yields error in rdrobust...
    waehlergruppen_majority == 1 ~ "waehlergruppen",
    TRUE ~ "neither cdu_csu nor waehlergruppen"
  )) %>%
  drop_na()
table(data_subset$state)
```
```{r, eval=FALSE}
# to do: remove eval=FALSE
all_values <- data_subset %>% distinct(abs_majority_party) %>% pull() # vector of values
rdd_vary_abs_majority <- # prepare data set to store the results
  tibble(abs_majority_party = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(2:last_col(), as.numeric))
for (i in all_values) {
  print(paste("abs_majority_party:", i))
  df <- data_subset %>%
    filter(abs_majority_party == i)
  rdd <-
    rdrobust_wrapper(
      ccluster = df$inhabitants_treshold_factor,
      ccovs = model.matrix( ~ df$inhabitants_treshold_factor + df$year) # FE
  )
  #summary(rdd)
  rdd_vary_abs_majority <- rdd_vary_abs_majority %>%
    dplyr::add_row(
      abs_majority_party = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_abs_majority <- rdd_vary_abs_majority %>% drop_na()
save(rdd_vary_abs_majority, file = "tables_robustness_checks/rdd_vary_abs_majority_by.Rdata")
rm(all_values, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_abs_majority_by.Rdata")
rdd_vary_abs_majority
```

```{r}
ggplot2::ggplot(data = rdd_vary_abs_majority, aes(x = abs_majority_party, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(rdd_vary_abs_majority$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(rdd_vary_abs_majority$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(rdd_vary_abs_majority$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Increase in spending at the threshold")
```

Interesting results for Bavaria: `cdu_csu` absolute majority drives up the treatment effect, whereas `waehlergruppen` as well as other majorities (including `spd` absolute majority and no single majority party) produce a contrary "Law of 1/n".

Interaction-term method using an IV approach:

```{r}
df <- data_subset %>%
  filter(closest <= 0.1)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*abs_majority_party ~
                       inhabs_rel_to_cutoff*above_cutoff*abs_majority_party,
                     vcov = "threeway",
                     data = df)
summary(rdd)
```
```{r}
rm(df)
```

Results from the `rdrobust` function cannot be reproduced: No significant differences from `cdu_csu` treatment effect in Bavaria.

### Export plot

```{r}
plot_council_majorities <- ggpubr::ggarrange(
  p_maj1,
  p_maj2,
  #labels = c("Absolute majority", "Absolute majority by party"),
  widths = c(2, 3),
  align = "h",
  ncol = 2,
  nrow = 1
) %>%
  annotate_figure(
    # See https://github.com/kassambara/ggpubr/issues/78
    left = text_grob("Increase in spending at the threshold", rot = 90)
    )
plot_council_majorities
ggsave(filename = "plots/rdd_absolute_majority_council.pdf", width = 6, height = 6*9/16)
```
```{r}
rm(p_maj1, p_maj2, lims)
```



## Digression: All expenditure categories

Run regressions over all expenditure categories

```{r, eval=FALSE}
# to do: remove eval=FALSE
exp_category <- data %>%
  select(starts_with("ln_expenditure")) %>% # select expenditure categories
  names() # pull their names
rdd_vary_exp_category <- # prepare data set to store the results
  tibble(exp_category = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(2:last_col(), as.numeric))
for (i in exp_category) {
  df <- data %>%
    select((!!rlang::sym(i)), inhabs_rel_to_cutoff, total_seats,
           inhabitants_treshold_factor, year, state) %>%
    drop_na()
  print(table(df$state))
  rdd <-
    rdrobust::rdrobust(
      y = df %>% pull(i),
      x = df$inhabs_rel_to_cutoff,
      fuzzy = df$total_seats,
      cluster = df$inhabitants_treshold_factor,
      covs = model.matrix(~ df$inhabitants_treshold_factor + df$year + df$state)
    )
  #summary(rdd)
  rdd_vary_exp_category <- rdd_vary_exp_category %>%
    dplyr::add_row(
      exp_category = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_exp_category <- rdd_vary_exp_category %>%
  drop_na() %>%
  mutate(exp_category2 = c("administrative", "administrative: personnel", "administrative: operating",
                           "capital", "capital: loans", "capital: property investment"))
save(rdd_vary_exp_category, file = "tables_robustness_checks/rdd_vary_exp_category.Rdata")
rm(df)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_exp_category.Rdata")
rdd_vary_exp_category
```

```{r}
df <- rdd_vary_exp_category %>%
  rowwise() %>%
  mutate(note = paste0(
    "n=",
    trimws(format(sum(obs_below, obs_above), big.mark = ",")),
    "\np=",
    round(p, 2)
    )) %>% 
  ungroup()
ggplot2::ggplot(data = df, aes(x = exp_category2, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  aes(stringr::str_wrap(exp_category2, 15)) +
  labs(x = NULL, y = "Increase in spending at the threshold") +
  geom_text(aes(y = -0.1, label = note),
            colour = ifelse(df$p <= p_value_cutoff, 2, 1), vjust = 0) #+
  #coord_flip()
ggsave(filename = "plots/rdd_exp_categories.pdf", width = 6, height = 6*9/16)
rm(df)
```

Not much variation in ATE across all spending categories.

IV approach:

```{r}
df <- data %>%
  filter(closest <= 0.1)
rdd <- fixest::feols(c(ln_expenditure_administrative_pc, ln_expenditure_admin_personel_pc,
                       ln_expenditure_adminoperating_pc, ln_expenditure_capital_pc, 
                       ln_expenditure_capital_loans_pc, ln_expenditure_capital_prop_inv_pc) ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats ~ # Instrument our standard RDD...
                       inhabs_rel_to_cutoff*above_cutoff, # ... with being above the cutoff
                     vcov = "threeway",
                     data = df)
summary(rdd)
```
```{r}
rm(df, exp_category)
```

Similar conclusions: No effect is significant at commonly used significance levels, lowest p value: 0.2.


## H11: More visible projects favored?

## H12: Social expenditures favored?

# Council characteristics

## H13: Female representation

### Overall data

Overall means 08 (BW) and 09 (BY)...

```{r, female_rep, eval=FALSE}
# to do: remove eval=FALSE
data_fem_rep1 <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor,
         state, year, female_share_council) %>%
  mutate(
    # female_share_council = ifelse(female_share_council > mean(data_by$female_share_council),
    #                               1,
    #                               0),
    female_share_council = cut(
      female_share_council,
      breaks = c(quantile(female_share_council, seq(0, 1, 0.25), na.rm = TRUE)),
      labels = FALSE
      )
  ) %>%
  drop_na()
table(data_fem_rep1$state)
data_fem_rep2 <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor,
         state, year, female_share_largest_party) %>%
  mutate(
    # female_share_largest_party = ifelse(female_share_largest_party >
    #                                       mean(data_by$female_share_largest_party),
    #                                     1,
    #                                     0),
    female_share_largest_party = cut(
      female_share_largest_party,
      breaks = c(quantile(female_share_largest_party, seq(0, 1, 0.25), na.rm = TRUE)),
      labels = FALSE
      )
  ) %>%
  drop_na()
table(data_fem_rep2$state)
data_fem_rep <-
  bind_rows(data_fem_rep1, data_fem_rep2)
all_values <- data_fem_rep %>% distinct(female_share_council) %>% drop_na() %>% pull() # vector of values
rdd_vary_fem_rep <- # prepare data set to store the results
  tibble(var = "", value = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(2:last_col(), as.numeric))
for (i in c("female_share_council", "female_share_largest_party")) {
  for (j in all_values) {
    print(paste("variable:", i, ", value:", j))
    df <- data_fem_rep %>%
      filter(!!rlang::sym(i) == j)
    rdd <-
      rdrobust::rdrobust(
        y = df$ln_gross_expenditure_pc,
        x = df$inhabs_rel_to_cutoff,
        fuzzy = df$total_seats,
        cluster = df$inhabitants_treshold_factor,
        covs = model.matrix(~ df$inhabitants_treshold_factor + df$year + df$state),
        level = (1-p_value_cutoff)*100
      )
    #summary(rdd)
    rdd_vary_fem_rep <- rdd_vary_fem_rep %>%
      dplyr::add_row(
        var = i,
        value = j,
        point_estimate = rdd$coef[1],
        se = rdd$se[1],
        se_robust = rdd$se[3],
        ci_lower = rdd$ci[3, 1],
        ci_upper = rdd$ci[3, 2],
        p = rdd$pv[3],
        bw = rdd$bws[1, 1],
        obs_below = rdd$N_h[1],
        obs_above = rdd$N_h[2]
      )
  }
}
rdd_vary_fem_rep <- rdd_vary_fem_rep %>% drop_na()
save(rdd_vary_fem_rep, file = "tables_robustness_checks/rdrobust_vary_fem_rep.Rdata")
rm(df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdrobust_vary_fem_rep.Rdata")
rdd_vary_fem_rep
```

```{r}
lims <- c(-0.14, 0.145)
rdd_vary_fem_rep <- rdd_vary_fem_rep %>%
  rowwise() %>%
  mutate(note = paste0(
    "n=",
    trimws(format(sum(obs_below, obs_above), big.mark = ",")),
    "\np=",
    round(p, 2)
    )) %>% 
  ungroup()
df1 <- rdd_vary_fem_rep %>% filter(var == "female_share_council")
df2 <- rdd_vary_fem_rep %>% filter(var == "female_share_largest_party")
p1 <- ggplot2::ggplot(data = df1, aes(x = value, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df1$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df1$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df1$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(limits = lims, labels = scales::percent) +
  geom_text(aes(y = -0.14, label = note),
            colour = ifelse(df1$p <= p_value_cutoff, 2, 1), vjust = 0) +
  labs(subtitle = "Share of women in council",
       x = "Quantile", y = "Increase in spending at the threshold")
p1
p1 <- p1 + labs(x = NULL, y = NULL)
p2 <- ggplot2::ggplot(data = df2, aes(x = value, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df2$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df2$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df2$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(limits = lims, labels = scales::percent) +
  geom_text(aes(y = -0.14, label = note),
            colour = ifelse(df2$p <= p_value_cutoff, 2, 1), vjust = 0) +
  labs(subtitle = "Share of women in the largest party",
       x = "Quantile of the heterogeneity-inducing variable", y = "Increase in spending at the threshold")
p2
p2 <- p2 + labs(x = NULL, y = NULL)
ggpubr::ggarrange(
  p1,
  p2,
  align = "h",
  ncol = 2,
  nrow = 1
  ) %>%
  annotate_figure(
    left = text_grob("Increase in spending at the threshold", rot = 90),
    bottom = text_grob("Quantile")
    )
ggsave(filename = "plots/rdd_council_women.pdf", width = 6, height = 6*9/16)
rm(df1, df2, lims, p1, p2)
```

Summary: Preliminary evidence from the `rdrobust` function indicates that councils with more men than average in the largest party have no effect but councils whose largest party has more than average women have a negative "Law of 1/n" effect. No effect for total council.

Hence, run IV interaction:

```{r}
df <- data %>%
  filter(closest <= 0.1) %>%
  mutate(state = as.factor(state))
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + year + state | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*female_share_council ~
                       inhabs_rel_to_cutoff*above_cutoff*female_share_council,
                     vcov = "threeway",
                     data = df)
summary(rdd)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + year + state | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*female_share_largest_party ~
                       inhabs_rel_to_cutoff*above_cutoff*female_share_largest_party,
                     vcov = "threeway",
                     data = df)
summary(rdd)
rm(df, rdd)
```

No effect visible using interaction-term method.


### Bavarian data

```{r, female_rep_by, eval=FALSE}
# to do: remove eval=FALSE
data_fem_rep_by <- data_by %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor,
         state, year, female_share_council, female_share_largest_party) %>%
  mutate(
    # female_share_council = ifelse(female_share_council > mean(data_by$female_share_council),
    #                               1,
    #                               0),
    female_share_council = cut(
      female_share_council,
      breaks = c(quantile(female_share_council, seq(0, 1, 0.25), na.rm = TRUE)),
      labels = FALSE
      ),
    # female_share_largest_party = ifelse(female_share_largest_party >
    #                                       mean(data_by$female_share_largest_party),
    #                                     1,
    #                                     0),
    female_share_largest_party = cut(
      female_share_largest_party,
      breaks = c(quantile(female_share_largest_party, seq(0, 1, 0.25), na.rm = TRUE)),
      labels = FALSE
      )
  ) %>%
  drop_na()
table(data_fem_rep_by$state)
all_values <- data_fem_rep %>% distinct(female_share_council) %>% drop_na() %>% pull() # vector of values
rdd_vary_fem_rep_by <- # prepare data set to store the results
  tibble(var = "", value = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(2:last_col(), as.numeric))
for (i in c("female_share_council", "female_share_largest_party")) {
  for (j in all_values) {
    print(paste("variable:", i, ", value:", j))
    df <- data_fem_rep_by %>%
      filter(!!rlang::sym(i) == j)
    rdd <-
      rdrobust::rdrobust(
        y = df$ln_gross_expenditure_pc,
        x = df$inhabs_rel_to_cutoff,
        #fuzzy = df$total_seats,
        cluster = df$inhabitants_treshold_factor,
        covs = model.matrix(~ df$inhabitants_treshold_factor + df$year + df$state)
      )
    #summary(rdd)
    rdd_vary_fem_rep_by <- rdd_vary_fem_rep_by %>%
      dplyr::add_row(
        var = i,
        value = j,
        point_estimate = rdd$coef[1],
        se = rdd$se[1],
        se_robust = rdd$se[3],
        ci_lower = rdd$ci[3, 1],
        ci_upper = rdd$ci[3, 2],
        p = rdd$pv[3],
        bw = rdd$bws[1, 1],
        obs_below = rdd$N_h[1],
        obs_above = rdd$N_h[2]
      )
  }
}
rdd_vary_fem_rep_by <- rdd_vary_fem_rep_by %>% drop_na()
save(rdd_vary_fem_rep_by, file = "tables_robustness_checks/rdrobust_vary_fem_rep_by.Rdata")
rm(df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdrobust_vary_fem_rep_by.Rdata")
rdd_vary_fem_rep_by
```

```{r}
df <- rdd_vary_fem_rep_by %>% mutate(x = paste(var, value))
ggplot2::ggplot(data = df, aes(x = x, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Year", y = "Increase in spending at the threshold")
rm(df)
```

Summary: Preliminary evidence from the `rdrobust` function indicates that councils with more men than average have no effect but councils with more than average women have a negative "Law of 1/n" effect.

Hence, run IV interaction:

```{r}
df <- data_by %>%
  filter(closest <= 0.1) %>%
  mutate(state = as.factor(state))
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*female_share_council ~
                       inhabs_rel_to_cutoff*above_cutoff*female_share_council,
                     vcov = "twoway",
                     data = df)
summary(rdd)
rm(df, rdd)
```

Here, there is no pattern.

```{r}
quants <- quantile(data_by$female_share_council, c(0.1, 0.9))
ggplot(data = data.frame(x = 0), mapping = aes(x = x)) +
  stat_function(fun = function(x) rdd_fem_rep1$coefficients[2] + rdd_fem_rep1$coefficients[3] + rdd_fem_rep1$coefficients[6] * x) +
  labs(x = "Share of female representatives in council") +
  xlim(quants)
rm(quants)
```

To be honest, the interpretation of the y axis is not really clear to me -- maybe leave out `fit_female_share_council` (that is `rdd_fem_rep1$coefficients[3]`) of the equation...?

Run the same setting for `female_share_largest_party`:

```{r}
df <- data_by %>%
  filter(closest <= 0.1) %>%
  mutate(state = as.factor(state))
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*female_share_largest_party ~
                       inhabs_rel_to_cutoff*above_cutoff*female_share_largest_party,
                     vcov = "twoway",
                     data = df)
summary(rdd)
rm(df, rdd)
```

Only significant at $\alpha$ = 0.1



# Municipality characteristics

## H14: Size of the municipalities

```{r, size_variation, eval=FALSE}
# to do: remove eval=FALSE
data_th <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year) %>%
  drop_na()
all_th <- data_th %>%
  distinct(inhabitants_treshold_factor) %>%
  filter(!(inhabitants_treshold_factor %in% c("45000", "35000", "60000", "75000", "80000", "150000", "2e+05", "250000", "3e+05", "4e+05", "5e+05", "550000", "7e+05"))) %>%
  pull() # vector of thresholds
rdd_vary_th <- # prepare data set to store the results
  tibble(threshold = "", states = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(c(1, 3:last_col()), as.numeric))
for (i in all_th) {
  print(paste("thresholds:", i))
  df <- data_th %>%
    filter(inhabitants_treshold_factor == i)
  states_in_df <- df %>% distinct(state) %>% pull()
  rdd <-
    rdrobust_wrapper(
      ccluster = NULL,
      ccovs = model.matrix( ~ df$year + df$state) # Dropping threshold FE
  )
  #summary(rdd)
  rdd_vary_th <- rdd_vary_th %>%
    dplyr::add_row(
      threshold = as.numeric(i),
      states = paste(states_in_df, collapse = ","),
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_th <- rdd_vary_th %>% drop_na() %>% arrange(threshold)
save(rdd_vary_th, file = "tables_robustness_checks/rdd_vary_th.Rdata")
rm(all_th, data_th, df, i, rdd, states_in_df)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_th.Rdata")
rdd_vary_th
```

Several thresholds, many of them rather large ones, have been dropped as they yield error messages from the `rdrobust` package, potentially owing to too few observations (close to the cutoff).

```{r}
df <- rdd_vary_th %>%
  filter(threshold != 100000)
ggplot2::ggplot(data = df, aes(x = threshold, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.1) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_x_log10() +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Population threshold", y = "Increase in spending at the threshold")
ggsave(filename = "plots/rdd_pop_size.pdf", width = 6, height = 6*9/16)
```

There are not many CI deviating from zero in a statistically significant way. This might also result from pooling several states in many of the cutoffs displayed above.

Interaction-term method using an IV approach with `inhabitants_threshold` included as a factor, not as a numerical variable:

```{r}
df <- data %>%
  filter(closest <= 0.1)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       year + state | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*inhabitants_treshold_factor ~
                       inhabs_rel_to_cutoff*above_cutoff*inhabitants_treshold_factor,
                     vcov = "twoway",
                     data = df)
summary(rdd)
# joint test on interactions
#fixest::wald(rdd, "fit_inhabs_rel_to_cutoff:inhabitants_treshold_factor")
# joint test fails: system is computationally singular
rm(df)
```

`inhabitants_threshold` numerical:

```{r}
df <- data %>%
  filter(closest <= 0.1)
# With threshold-FE
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + year + state | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*inhabitants_treshold ~
                       inhabs_rel_to_cutoff*above_cutoff*inhabitants_treshold,
                     vcov = "twoway",
                     data = df)
summary(rdd)
# Without threshold-FE
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       year + state | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*inhabitants_treshold ~
                       inhabs_rel_to_cutoff*above_cutoff*inhabitants_treshold,
                     vcov = "twoway",
                     data = df)
summary(rdd)
rm(df)
```



## H15: Kreisfreie Städte vs. not

General remark: The two variables `kreisfreie_stadt` and `stadt` are mutually exclusive. If a city is categorized as a "district-free city" (`kreisfreie_stadt == 1`), `stadt == 1`. So each town belongs to one of three categories:

- `kreisfreie_stadt = 0` & `stadt = 0` -> "Gemeinde"/municiapality
- `kreisfreie_stadt = 0` & `stadt = 1` -> "kreisangehörige Stadt"/town within a county
- `kreisfreie_stadt = 1` & `stadt = 1` -> "kreisfreie Stadt"/"district-free city"


```{r}
data_subset <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year, kreisfreie_stadt, stadt, closest, above_cutoff) %>%
  drop_na() %>%
  mutate(
    status = case_when(
      as.numeric(kreisfreie_stadt) == 1 & as.numeric(stadt) == 1 ~ "municipality",
      as.numeric(kreisfreie_stadt) == 1 & as.numeric(stadt) == 2 ~ "town",
      as.numeric(kreisfreie_stadt) == 2 & as.numeric(stadt) == 1 ~ "district-free city"
    )
  )
table(data_subset$state)
```
```{r, eval=FALSE}
all_values <- data_subset %>% distinct(status) %>% pull() # vector of values
rdd_vary_city <- # prepare data set to store the results
  tibble(status = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(2:last_col(), as.numeric))
for (i in all_values) {
  print(paste("status:", i))
  df <- data_subset %>%
    filter(status == i)
  rdd <-
    rdrobust_wrapper(
      ccluster = df$inhabitants_treshold_factor,
      ccovs = model.matrix( ~ df$inhabitants_treshold_factor + df$state) # Dropping year FE
  )
  #summary(rdd)
  rdd_vary_city <- rdd_vary_city %>%
    dplyr::add_row(
      status = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_city <- rdd_vary_city %>% drop_na()
save(rdd_vary_city, file = "tables_robustness_checks/rdd_vary_city.Rdata")
rm(all_values, df, i, rdd)
```
```{r}
load(file = "tables_robustness_checks/rdd_vary_city.Rdata")
rdd_vary_city
```

```{r}
 df <- rdd_vary_city %>%
  rowwise() %>%
  mutate(note = paste0(
    "n=",
    trimws(format(sum(obs_below, obs_above), big.mark = ",")),
    "\np=",
    round(p, 2)
    )) %>%
  ungroup()
ggplot2::ggplot(data = df, aes(x = reorder(status, c(1, 3, 2)), y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(df$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(df$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(df$p <= p_value_cutoff, 2, 1),
                width = 0.25) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  geom_text(aes(y = -0.315, label = note),
            colour = ifelse(df$p <= p_value_cutoff, 2, 1), vjust = 0) +
  labs(x= NULL, y = "Increase in spending at the threshold")
ggsave(filename = "plots/rdd_cities.pdf", width = 6, height = 6*9/16)
```

No significant effect visible.


Interaction-term method using an IV approach with `year` included as a factor, not as a numerical variable:

```{r}
df <- data_subset %>% # Use data set from above
  filter(closest <= 0.1)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*status ~ # Instrument our standard RDD...
                       inhabs_rel_to_cutoff*above_cutoff*status, # ... with being above the cutoff
                     vcov = "threeway",
                     data = df)
summary(rdd)
# joint test on interactions
fixest::wald(rdd, "fit_total_seats:status")
```
```{r}
rm(data_subset, df, rdd)
```

Extremely high p value for the joint test: No significant differences from baseline ("district-free cities").






# Model procedure

Subsample method:

```{r, eval=FALSE}
# to do: remove eval=FALSE
data_subset <- data %>% # prepare data set used for analysis
  select(ln_gross_expenditure_pc, inhabs_rel_to_cutoff, total_seats, inhabitants_treshold_factor, state, year, kreisfreie_stadt, stadt) %>%
  drop_na()
all_values <- data_subset %>% distinct(kreisfreie_stadt) %>% pull() # vector of values
rdd_vary_city <- # prepare data set to store the results
  tibble(value = "", point_estimate = "", se = "", se_robust = "",
         ci_lower = "", ci_upper = "", p = "", bw = "", obs_below = "", obs_above = "") %>%
  mutate(across(everything(), as.numeric))
for (i in all_values) {
  print(paste("year:", i))
  df <- data_subset %>%
    filter(year == i)
  rdd <-
    rdrobust_wrapper(
      ccluster = df$inhabitants_treshold_factor,
      ccovs = model.matrix( ~ df$inhabitants_treshold_factor + df$state + df$year) # FE
  )
  #summary(rdd)
  rdd_vary_city <- rdd_vary_city %>%
    dplyr::add_row(
      value = i,
      point_estimate = rdd$coef[1],
      se = rdd$se[1],
      se_robust = rdd$se[3],
      ci_lower = rdd$ci[3,1],
      ci_upper = rdd$ci[3,2],
      p = rdd$pv[3],
      bw = rdd$bws[1,1],
      obs_below = rdd$N_h[1],
      obs_above = rdd$N_h[2]
  )
}
rdd_vary_city <- rdd_vary_city %>% drop_na()
save(rdd_vary_city, file = "tables_robustness_checks/rdd_vary_city.Rdata")
rm(all_values, data_subset, df, i, rdd)
```
```{r, eval=FALSE}
load(file = "tables_robustness_checks/rdd_vary_city.Rdata")
rdd_vary_city
```

```{r, eval=FALSE}
ggplot2::ggplot(data = rdd_vary_city, aes(x = value, y = point_estimate)) +
  geom_point(size = 1.5, color = ifelse(rdd_vary_city$p <= p_value_cutoff, 2, 1)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                color = ifelse(rdd_vary_city$p <= p_value_cutoff, 2, 1),
                linetype = ifelse(rdd_vary_city$p <= p_value_cutoff, 2, 1),
                width = 0.5) +
  geom_hline(aes(yintercept = 0), linetype = "dotted") +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "Increase in spending at the threshold")
```

*Preliminary conclusion here*


Interaction-term method using an IV approach:

```{r, eval=FALSE}
df <- data %>%
  filter(closest <= 0.1)
rdd <- fixest::feols(ln_gross_expenditure_pc ~
                       1  | # controls
                       inhabitants_treshold_factor + state + year | # fixed-effect controls
                       # First stage regression:
                       inhabs_rel_to_cutoff*total_seats*year ~ # Instrument our standard RDD...
                       inhabs_rel_to_cutoff*above_cutoff*year, # ... with being above the cutoff
                     vcov = "threeway",
                     data = df)
summary(rdd)
# joint test on interactions
fixest::wald(rdd, "fit_total_seats:year")
#rm(df)
```

*Conclusion*





# Concluding Remarks

For references, see the paper.

```{r}
Sys.time() - time
```
