---
author: "Florian Fox"
date: "`r Sys.Date()`"
title: 'Master Thesis: A Causal Test of the Law of 1/n and its Mechanisms -- Descriptive Statistics'
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

# Load data and packages

```{r Packages}
library(tidyverse)
library(reshape2)
```

```{r Data}
data <-
  readRDS("data/gemeinderatswahlen_alldata.rds")
```

```{r Options}
options(scipen = 20)
theme_set(theme_minimal())
```



# First look at the data

```{r First look}
glimpse(data)
```

# Univariat statistics

## NAs

```{r}
data %>%
  summarize(across(.cols = everything(),
                   .fns = ~sum(is.na(.))/n()
                   ))
data %>%
  group_by(state) %>%
  summarize(across(.cols = everything(),
                   .fns = ~sum(is.na(.))/n()
                   ))
data %>%
  group_by(year) %>%
  summarize(across(.cols = everything(),
                   .fns = ~sum(is.na(.))/n()
                   ))
data %>%
  group_by(state, year) %>%
  summarize(across(.cols = everything(),
                   .fns = ~sum(is.na(.))/n()
                   ))
```


## Numeric variables

```{r}
summarize2 <- function(x, na.rm = TRUE) {
  result <- c(
    Min = min(x, na.rm = na.rm),
    Q25 = quantile(x, probs = 0.25, na.rm = na.rm),
    Median = median(x, na.rm = na.rm),
    Q75 = quantile(x, probs = 0.75, na.rm = na.rm),
    Max = max(x, na.rm = na.rm),
    Mean = mean(x, na.rm = na.rm),
    SD = sd(x, na.rm = na.rm),
    No_of_unique_values = n_distinct(x),
    N = length(x) - sum(is.na(x)),
    No_NA = sum(is.na(x))
  )
}
```
```{r Univariate stats}
dim(data)
data %>%
  summarize(
    across(
      where(is.numeric),
      summarize2
    )
  ) %>%
  mutate(Stat = c("Min", "1st Quar", "Median", "3rd Quar", "Max", "Mean", "SD", "No of unique values", "n", "No of NA"),
         .before = No)
```


## Factors


```{r}
data %>%
  select(-where(is.numeric), -starts_with("ags"), -town) %>%
  sapply(., function(x) table(x, useNA = "always"))
```

# Bivariate descriptive statistics



Display correlation between standard council size (as determined (by me) by council size) with actual number of seats. Especially weak in Baden-Württemberg, North-Rhine Westphalia, and Saxony. Strong in Saarland (sharp design here), Thuringia, and Brandenburg (though few data points here).

```{r, rows.print=15}
data %>%
  group_by(state) %>%
  summarize(n = n(), seat_cor = cor(total_seats, by_law_seats, use = "pairwise.complete.obs")) %>%
  arrange(seat_cor)
```


```{r}

```

